Improved Bounds for Online Balanced Repartitioning

### 2020-05-01 paper/disc20clustering.tex
Comments
Distributed k=2 sketch

\maciek{"We charge OPT the cost
$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}[1,t]) 
\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
for collocating this pair or (and) paying (partially) for requests in $\sigma_{\{u,v\}}[1,t]$." No issues with charge sharing from "regular collocation" case? Maybe I just don't understand "partially" here}

@@

\maciek{Structure in paragraphs. 3 parts: first collocation, regular collocation and unfinished. Do this for ALG and then for OPT, and do not mix (unless I don't see some dependencies). Start each paragraph by the sentence that says what the paragraph is about (first/opt, regular/alg etc.). Assume that the reader reads only the first sentence of each paragraph (if it's short), and the proof must be clear from this (for a professional)}

@@

>>>>

\maciek{"We charge OPT the cost
$\mathit{Cost}_{\mathit{OPT}} (\sigma_{\{u,v\}}[1,t]) 
\geq \min{ \{ \alpha, C^{m}_{ \{u,v\} } \} }$,
for collocating this pair or (and) paying (partially) for requests in $\sigma_{\{u,v\}}[1,t]$." No issues with charge sharing from "regular collocation" case? Maybe I just don't understand "partially" here. Not necessarily rewrite! Just maybe check if it's true.}

@@

\maciek{Structure in paragraphs. 3 parts: first collocation, regular collocation and unfinished. Do this for ALG and then for OPT, and do not mix (unless I don't see some dependencies). Start each paragraph by the sentence that says what the paragraph is about (first/opt, regular/alg etc.). Assume that the reader reads only the first sentence of each paragraph (if it's short), and the proof structure must be clear from this. Some other important things go to their own paragraph too, and the first sentence must describe what we do there.}

@@

\subsection{Distributed implementation of $k=2$ algorithm}

For a repartition, it is sufficient to find the cluster with the signature $1,1,1$. 
We call any such cluster \emph{X (todo name)}.
Idea of distributed implementation of this procedure:
\begin{enumerate}
	\item Assign ids to clusters and order them
	\item Recursively partition clusters into two groups
	\item Each group maintains the pointer to a subgroup that contains at least one X cluster; a pointer may be null (then no X there)
	\item This way, finding a cluster X requires $\log_2(\ell)$ communication
	\item After removing an X cluster, we need to fix the pointers. This is done by following the path from the removed X cluster to the root. We simply ask the sibling if it contains X.
\end{enumerate}
